Improving the Reliability of the Pavlovian Go/No-Go Task

### 2023-04-25 manuscript/main.tex
checkpointing manuscript progress (4)

% load packages
\usepackage[utf8]{inputenc}
\usepackage[a4paper, margin=0.8in]{geometry}
\usepackage[english]{babel}
\usepackage{authblk}
\usepackage[backend=biber,style=nature]{biblatex}    % citation management
\usepackage[font=small, labelfont=it]{caption}       % figure/table captions
\usepackage{float, graphicx, svg}                    % figure/table management
\usepackage[pagewise]{lineno}                        % add line numbers for reviewers
\usepackage{indentfirst}                             % for pretty paragraphs
\usepackage{booktabs}                                % for pretty tables
\usepackage{hyperref}                                % for pretty links
\usepackage{amsmath}                                 % for pretty equations

@@

Humans (and other animals) have an innate tendency to approach rewarding stimuli and shrink from punishing stimuli \cite{carver1994behavioral}. These inflexible Pavlovian biases can benefit or interfere with instrumental (i.e., action-outcome) learning depending on the context. For example, in a Pavlovian go/no-go task that orthogonalizes action (go, no-go) and valence (reward, punishment), human participants make more correct responses on Pavlovian-instrumental congruent trials where they must initiate action to receive reward or inhibit action to avoid punishment than on Pavlovian-instrumental incongruent trials where they must inhibit action to receive reward or initiate action to avoid punishment \cite{guitart2012go, guitart2014action}. The Pavlovian-instrumental interactions observed in task performance may arise during action selection (i.e., rewarding and punishing stimuli potentiate and inaction, respectively; \cite{guitart2012go}) and during learning (i.e., learning more rewards following action and punishments following inaction; \cite{swart2017catecholaminergic}).

Individual-differences in the expression of Pavlovian biases on the Pavlovian go/no-go task have been the focus of numerous studies. Pavlovian biases have been observed to vary as a function of many psychiatric conditions. For example, individuals with general and social anxiety show an increased bias towards passive avoidance behavior \cite{mkrtchian2017modeling, peterburs2021impact}, whereas active avoidance is amplified in individuals with a history of suicidal thoughts or behaviors \cite{millner2019suicidal}.  Pavlovian biases are enhanced for individuals with trauma exposure \cite{ousdal2018impact} and first-episode psychosis \cite{montagnese2020reinforcement}, but attenuated in individuals with depression \cite{huys2016specificity} and schizophrenia \cite{albrecht2016reduction}. Pavlovian biases have also been observed to vary parabolically across the lifespan, with decreasing bias from childhood to young adulthood which increases again in older age \cite{raab2020adolescents, betts2020learning}. Pavlovian biases have been associated with individual differences in personality \cite{eisinger2020pavlovian} and genetics \cite{richter2014valenced, richter2021motivational} (but see also \cite{montagnese2020reinforcement}). Pavlovian biases are also modulated by differences in acute state, such as current mood \cite{weber2022effects}, anger \cite{wonderlich2020anger}, stress \cite{de2016acute}, and fear \cite{mkrtchian2017threat}.

None of the individual-difference studies above, however, investigated or reported the reliability of their task measures. This is important because the reliability of a measure places an upper bound on the maximum observable correlation between itself and a second measure (e.g., symptom scores; \cite{zorowitz2023improving}). As an important corollary, as the reliability of a task measure decreases, so too does the power to detect individual-difference correlations, which increases the possibility of false-negative results \cite{Parsons2019-jw} and bias in effects that do reach statistical significance \cite{gelman2014beyond}. What studies that do exist suggest that the reliability of performance measures on the Pavlovian go/no-go task are poor. Moutoussis and colleagues \cite{moutoussis2018change} studied the psychometrics of the task in a large cohort of adolescents and young adults and found that both descriptive and model-based behavioral measures exhibited poor test-retest reliability. It was unclear, however, if this finding reflected the developmental sample and/or their lengthy test-retest intervals (6 and 18 months). Recently, Pike and colleagues \cite{pike2022test} investigated reliability of descriptive and model-based behavioral Pavlovian go/no-go task measures in an online adult sample over a 2-week test-retest interval. Regardless, they too found unacceptable reliability. Thus, the current state of the literature suggests that the Pavlovian go/no-go task is poorly suited for use in individual-differences studies.

A second psychometric consideration is task repeatability, or the ability of task to consistently elicit an expected pattern of behavior across repeated administrations. One concern for task repeatability is practice effects, where participants’ performance on a task improves with increasing exposure. Practice effects are relatively common for cognitive tasks \cite{hausknecht2007retesting, scharfen2018retest}. The repeatability of the Pavlovian go/no-go task has received less attention, though Moutoussis and colleagues reported that task performance improved and Pavlovian biases decreased over both 6 and 18 month follow-ups \cite{moutoussis2018change}. Practice effects can be confounding in longitudinal studies, especially for studies where an experimenter would expect reductions in bias (e.g., avoidance biases following a psychotherapy intervention). Moreover, practice effects can hamper diminish reliability if they manifest differentially across participants or if they minimize between-participant variability due to ceiling effects.

The objective of the present study was to investigate the reliability and repeatability of a gamified version of the Pavlovian go/no-go task. Gamification, or the incorporation of (video) game design elements into cognitive tasks, can increase participant engagement \cite{sailer2017gamification} and has previously been found to improve the reliability of task measures \cite{kucina2022solution, verdejo2021unified}. In Experiment 1, a sample of N=103 participants completed the gamified task four times over one month. We used reinforcement learning models quantify Pavlovian biases in choice behavior. Contrary to our expectations, we observed large practice effects in participants' performance, including the virtual disappearance of Pavlovian biases, that in turn impacted the reliability of estimated model parameters. In Experiment 2, a sample of N=110 participants completed a modified version of the Pavlovian go/no-go task --- one that prevents participants from using alternative strategies to complete the task --- three times over two weeks. Here we observed comparably smaller practice effects and, crucially, acceptable reliability of estimated model parameters.

@@

A total of N=148 participants were recruited from Amazon Mechanical Turk (via CloudResearch; \cite{litman2017turkprime}) in May, 2020 to participate in an online behavioral experiment. Participants were eligible to participate if they were at least 18 years old and resided in the United States. Following best practice recommendations \cite{robinson2019tapped}, no other inclusion criteria were applied. This study was approved by the Institutional Review Board of Princeton University (\#5291), and all participants provided informed consent. Total study duration was 15-20 minutes. Participants received monetary compensation for their time (rate: USD \$12/hr), plus an incentive-compatible bonus up to \$1.50 based on task performance.

@@

In each session, participants started by completing several self-report questionnaires (see Supplementary Materials for details). These measures were included for exploratory analyses that are not reported here. Next, participants completed a gamified version of the Pavlovian go/no-go task \cite{guitart2012go, swart2017catecholaminergic}. In the task, participants observed different `robot' stimuli (Figure \ref{fig:task_schematic}A). On every trial, a robot was shown traveling down a conveyer belt into a `scanner'. Once inside, participants had 1.5 seconds to decide to either `repair' the robot by pressing the space bar (go response) or press nothing (no-go response). Participants were told that they would see different types of robots (indicated by a symbol on the robots' chestplates), and that their goal was to learn the correct response (go, no-go) for each robot type based on feedback (points won/lost) following each action.

The task involved four trial types that differed in their correct action (go, no-go) and outcome domain (reward, punishment; Figure \ref{fig:task_schematic}B). Specifically, the four trial types were: go to win points (GW); no-go to win points (NGW); go to avoid losing points (GAL); and no-go to avoid losing points (NGAL). Note that GW and NGAL trials are Pavlovian-instrumental `congruent' because there is a match between the correct response and the approach/avoidance biases for each, whereas NGW and GAL trials are Pavlovian-instrument `incongruent'. For the rewarding trials (GW, NGW), the possible outcomes were +10 or +1 points; for the punishing trials (GAL, NGAL), they were -1 or -10 points. The outcome domain of each robot was explicitly signaled to participants by a blue or orange `scanner light' (randomized across sessions). Outcomes were probabilistic such that participants received the better of the possible outcomes with 80\% chance if they made the correct action, and received the worse of the possible outcomes with 80\% chance if they made the incorrect action (Figure \ref{fig:task_schematic}C).

Participants saw eight unique robots across the task. Each individual robot was presented for 30 trials (240 trials total; Figure \ref{fig:task_schematic}D). Trials were divided into two blocks with four robots (one of each trial type) per block. Prior to task start, participants were required to review instructions, correctly answer five comprehension questions, and complete several practice trials. Failing to correctly answer all comprehension items forced the participant to reread sections of the instructions. Participants were provided a break between blocks. The task was programmed in jsPsych \cite{de2015jspsych} and distributed using custom web-application software (see Code Availability).

@@

We first evaluated participants' choice behavior using five performance indices: overall percent correct responses; go bias, or the difference in correct responses between go and no-go trials; domain bias, or the difference in correct responses between rewarding and punishing trials; Pavlovian bias, or the difference in correct responses between Pavlovian congruent and incongruent trials; and feedback sensitivity, or the difference in correct responses between trials following veridical or sham feedback. Within each session, we tested if the median value across participants for each index was significantly different than zero (or 50\% for overall percent correct responses). We use the median due to the skew in the performance indices (see Results). We also tested if the median value of each index was significantly different between each pair of sessions. P-values were derived via permutation testing, where a null distribution of values were obtained by permuting the condition labels (for within-session tests) or day labels (for between-session tests) 5000 times. Within-session tests were not corrected for multiple comparisons because each test constitutes an individual hypothesis; between-session tests were corrected for multiple comparisons using the familywise error rate correction \cite{winkler2014permutation}.

@@

We fit a set of seven nested reinforcement learning (RL) models to participants' choice data. All models are variants of the Rescorla-Wagner model and have previously been used to predict choice behavior on this task \cite{guitart2012go, mkrtchian2017modeling, moutoussis2018change, swart2017catecholaminergic}. In the base model (M1), the probability of choosing an action is determined by the difference in stimulus-action values, scaled an outcome sensitivity parameter ($\beta$), and passed through the logistic function. In turn, action values are learned via the Rescorla-Wagner update rule as governed by a learning rate ($\eta$). The next model (M2) is augmented with a static approach/avoidance parameter ($\tau$) that biases action towards go and no-go responses when $\tau > 0$ and $\tau < 0$, respectively. The next model (M3) has independent approach/avoidance parameters per outcome domain ($\tau_+$, $\tau_-$). The succeeding models have either independent outcome sensitivity  ($\beta_+$, $\beta_-$; M4) or learning rate parameters ($\eta_+$, $\eta_-$; M5) per outcome domain. The penultimate model (M6) separates all three parameter types by outcome domain. Finally, the most complex model (M7) adds a lapse rate ($\xi$). Full equations and model descriptions are provided in the Supplementary Materials.

@@

Trial-by-trial choice behavior for each session is presented in Figure \ref{fig:exp01_behavior}A. Performance in the first session qualitatively conformed to the expected pattern of results, namely worse performance on Pavlovian incongruent trials. This effect was seemingly diminished, however, in all follow-up sessions. We turn next to the descriptive analyses to formally evaluate these observations.

The group-averaged performance indices per session are summarized in Figure \ref{fig:exp01_behavior}B. On Day 0, the overall percent correct responses was 85.0\% ($d = 2.982$, $p < 0.001$, 95\% CI = [80.8, 87.9]). Performance improved in all subsequent sessions (Day 3: M = 92.9\%, $d = 6.947$, $p < 0.001$, 95\% CI = [90.4, 94.6]; Day 14: 94.6\%, $d = 10.310$, $p < 0.001$, 95\% CI = [93.1, 95.2]; Day 28: 94.6\%, $d=12.029$, $p < 0.001$, 95\% CI = [93.8, 95.8]). Pairwise comparisons confirmed that performance was indeed worse on Day 0 compared to each follow-up session (all $p < 0.001$); no other comparisons were significant. Participants' self-reported mood and anxiety were largely stable over the same period (Figure \ref{fig:figS05}), suggesting this shift in performance reflects practice effects and not changes in participants' state.

Across sessions, participants made more correct responses on go trials than no-go trials (Day 0: $\Delta$M = 0.117, $d = 1.049$, $p < 0.001$, 95\% CI = [0.108, 0.133]; Day 3: $\Delta$M = 0.050, $d = 1.156$, $p < 0.001$, 95\% CI = [0.042, 0.058]; Day 14: $\Delta$M = 0.042, $d = 1.124$, $p < 0.001$, 95\% CI = [0.029, 0.046]; Day 28: $\Delta$M = 0.033, $d = 0.899$, $p < 0.001$, 95\% CI = [0.025, 0.042]). The go bias was significantly reduced in all follow-up sessions compared to Day 0 (all $p < 0.001$); so too was the bias on Day 28 compared to Day 3 ($p < 0.001$). Similarly, participants made more correct responses on Pavlovian-congruent than incongruent trials (Day 0: $\Delta$M = 0.092, $d = 1.237$, $p < 0.001$, 95\% CI = [0.067, 0.117]; Day 3: $\Delta$M = 0.017, $d = 0.450$, $p < 0.001$, 95\% CI = [0.008, 0.025]; Day 14: $\Delta$M = 0.017, $d = 0.450$, $p < 0.001$, 95\% CI = [0.008, 0.025]; Day 28: $\Delta$M = 0.008, $d = 0.225$, $p < 0.001$, 95\% CI = [0.000, 0.017]). Again, the Pavlovian bias was significantly reduced in all follow-up sessions compared to Day 0 (all $p < 0.001$); no other comparisons were significant. Participants made marginally more correct responses on rewarding trials on Day 3 only ($\Delta$M = 0.008, $d=0.169$, $p = 0.017$, 95\% CI = [0.000, 0.025]).

@@

Trial-by-trial choice behavior for each session is presented in Figure \ref{fig:exp02_behavior}A. In contrast to Experiment 1, performance in each session qualitatively conformed to the expected pattern of results. The group-averaged performance indices per session are summarized in Figure \ref{fig:exp02_behavior}B. On Day 0, overall percent correct responses was 67.5\% ($d = 1.828$, $p < 0.001$, 95\% CI = [65.8, 69.0]). Performance improved in all subsequent sessions, but only marginally so (Day 3: M = 71.7\%, $d = 2.063$, $p < 0.001$, 95\% CI = [69.6, 74.6]; Day 14: 69.6\%, $d = 1.441$, $p < 0.001$, 95\% CI = [66.5, 73.8]). Pairwise comparisons confirmed that performance was significantly greater on Day 3 compared to Day 0 ($p = 0.009$); however, no other comparisons were significant.

@@

In all sessions, participants performed better on go trials than no-go trials (Day 0: $\Delta$M = 0.192, $d = 1.108$, $p < 0.001$, 95\% CI = [0.150, 0.225]; Day 3: $\Delta$M = 0.133, $d = 0.899$, $p < 0.001$, 95\% CI = [0.100, 0.150]; Day 14: $\Delta$M = 0.142, $d = 0.882$, $p < 0.001$, 95\% CI = [0.075, 0.175]). The go bias on Day 0 was significantly greater than that for all other sessions (all $p < 0.005$); no other comparisons were significant. Participants also performed better on Pavlovian congruent compared to incongruent trials in all sessions (Day 0: $\Delta$M = 0.125, $d = 1.065$, $p < 0.001$, 95\% CI = [0.100, 0.150]; Day 3: $\Delta$M = 0.083, $d = 0.843$, $p < 0.001$, 95\% CI = [0.067, 0.100]; Day 14: $\Delta$M = 0.075, $d = 0.867$, $p < 0.001$, 95\% CI = [0.050, 0.092]). The Pavlovian bias on Day 0 was significantly greater than that for all other sessions (both $p = 0.027$); no other comparisons were significant. In sum, group-averaged behavior showed evidence of practice effects but these were minor by comparison to those observed in Experiment 1.

A similar pattern of results was observed for feedback sensitivity. Across sessions, participants made more correct responses following veridical compared to sham feedback (Day 0: $\Delta$M = 0.282, $d = 2.254$, $p < 0.001$, 95\% CI = [0.257, 0.309]; Day 3: $\Delta$M = 0.294, $d = 2.142$, $p < 0.001$, 95\% CI = [0.247, 0.320]; Day 14: $\Delta$M = 0.268, $d = 2.267$, $p < 0.001$, 95\% CI = [0.241, 0.294]). No pairwise comparison was significant (all $p > 0.10$), suggesting that feedback sensitivity was largely conserved across sessions.

@@

The current study is not without limitations. Here we have only investigated the psychometric properties of our modified Pavlovian go/no-go task in a sample of online adult participants. The reliability of task measures, however, are not absolute; reliability can vary by participant demographics and the experiment setting. For example, previous studies have found that the reliability of specific task measures in healthy adults is not the same as for adults with psychopathology \cite{cooper2017role} or healthy children \cite{arnon2020current}. To the extent that our modified version of the Pavlovian go/no-go task is more challenging (see \ref{tab:tabS02}), it may be the case that it proves too challenging for other groups, which may harm reliability (e.g., \cite{arnon2020current}). Additional studies are necessary to validate this version of the task in other populations. It should also be noted that the current study is not necessarily informative about the reliability of Pavlovian biases over longer periods of time (i.e., beyond 2--4 weeks).

@@

@@

\begin{table}[h!]
    \centering
    \begin{tabular}{lccccc}
    \toprule
               & Study &   Day 0 &      Day 3 &     Day 14 &     Day 28 \\
    \midrule
    Difficulty &  1 &  2.5 (1.1) &  2.2 (0.9) &  2.1 (1.0) &  1.8 (0.8) \\
               &  2 &  3.3 (1.1) &  3.0 (1.1) &  3.1 (1.1) &          - \\
    \midrule
    Fun        &  1 &  3.9 (0.9) &  4.0 (1.0) &  3.9 (0.9) &  4.1 (0.9) \\
               &  2 &  3.9 (0.9) &  4.1 (0.8) &  4.0 (0.8) &          - \\
    \midrule
    Clarity    &  1 &  4.8 (0.6) &  4.9 (0.4) &  5.0 (0.2) &  4.9 (0.3) \\
               &  2 &  4.9 (0.5) &  4.9 (0.2) &  4.9 (0.2) &          - \\
    \bottomrule
    \end{tabular}
    \caption{Mean (sd) of participants' ratings of task difficulty, fun, and clarity. All ratings were made on a 5-point Likert scale. Difficulty: ``How difficult was the task?'' (Very easy = 1, Very hard = 5); Fun: ``How fun was the task?'' (Very boring = 1, Very fun = 5); Clarity: ``How clear were the instructions?'' (Very confusing = 1, Very Clear = 5).}
    \label{tab:tabS02}
\end{table}

@@

>>>>

% load packages
\usepackage[utf8]{inputenc}
\usepackage[a4paper, margin=0.8in]{geometry}
\usepackage[english]{babel}
\usepackage{authblk}
\usepackage[backend=biber,style=nature]{biblatex}    % citation management
\usepackage[font=small, labelfont=it]{caption}       % figure/table captions
\usepackage{float, graphicx, svg}                    % figure/table management
\usepackage[pagewise]{lineno}                        % add line numbers for reviewers
\usepackage{indentfirst}                             % for pretty paragraphs
\usepackage{booktabs}                                % for pretty tables
\usepackage{hyperref}                                % for pretty links
\usepackage{amsmath}                                 % for pretty equations
\usepackage[export]{adjustbox}                       % center wide tables on page

@@

Humans (and other animals) have an innate tendency to approach rewarding stimuli and shrink from punishing stimuli \cite{carver1994behavioral}. Depending on the context, these hardwired Pavlovian biases can benefit or interfere with instrumental (i.e., action-outcome) learning. This is epitomized in a Pavlovian go/no-go task that orthogonalizes action (Go, No-Go) and outcome valence (reward, punishment) \cite{guitart2012go, guitart2014action}. On the task, human participants are faster to learn actions that are congruent with these Pavlovian response biases (i.e., initiate action to receive reward, inhibit action to avoid punishment) and slower to learn Pavlovian-instrumental incongruent responses (i.e., inhibit action to receive reward, initiate action to avoid punishment). These biases can arise during action selection \cite{guitart2012go} and learning (i.e., increased sensitivity to rewards and punishments following action and inaction, respectively; \cite{swart2017catecholaminergic}).

Individual-differences in performance on the Pavlovian go/no-go task have been the focus of many studies. Pavlovian biases are altered in a number of psychiatric conditions. For example, an increased tendency towards passive avoidance has been observed in individuals with general and social anxiety \cite{mkrtchian2017modeling, peterburs2021impact}, whereas active avoidance is amplified in individuals with a history of suicidal thoughts or behaviors \cite{millner2019suicidal}.  Pavlovian biases are larger in individuals with trauma exposure \cite{ousdal2018impact} and first-episode psychosis \cite{montagnese2020reinforcement}, but attenuated in individuals with depression \cite{huys2016specificity} and schizophrenia \cite{albrecht2016reduction}. Pavlovian biases exhibit a U-shape across the lifespan, decreasing from childhood to young adulthood and increasing again in older age \cite{raab2020adolescents, betts2020learning}. Pavlovian biases have been associated with individual differences in personality (e.g., impulsivity; \cite{eisinger2020pavlovian}) and genetic polymorphisms \cite{richter2014valenced, richter2021motivational}. The expression of Pavlovian biases are also modulated by differences in current state, such as mood \cite{weber2022effects}, anger \cite{wonderlich2020anger}, stress \cite{de2016acute}, and fear \cite{mkrtchian2017threat}.

None of the studies above investigated or reported the reliability of their task performance measures. This is important because the reliability of a measure places an upper bound on the maximum observable correlation between itself and a second measure (e.g., symptom scores; \cite{zorowitz2023improving}). Therefore, as the reliability of a task measure decreases, so too does the power to detect and precisely estimate individual-difference correlations, which in turn increases the possibility of false-negatives \cite{Parsons2019-jw} and bias in correlations reaching statistical significance \cite{gelman2014beyond}. To date, two studies have investigated the psychometrics of the Pavlovian go/no-go task. In a large study of adolescents and young adults, Moutoussis and colleagues \cite{moutoussis2018change} found that both descriptive and model-based measures of performance on the task exhibited poor test-retest reliability. It was unclear, however, if this finding reflected their sample population and/or their lengthy test-retest intervals (6 and 18 months). However, Pike and colleagues \cite{pike2022test} recently reported similar results in an online sample of adults tested twice over over two weeks. Thus, the extant literature indicates performances measures on the Pavlovian go/no-go task are poorly suited for use in individual-differences research.

A second psychometric consideration is task repeatability, or the ability for a task to consistently elicit an expected pattern of behavior across repeated administrations. One common threat to task repeatability is practice effects, where participants’ performance on a task improves with increasing exposure \cite{hausknecht2007retesting, scharfen2018retest}. Practice effects may confound longitudinal studies of task performance, especially studies in which an improvement in performance is hypothesized (e.g., reduction in Pavlovian biases following a psychotherapy intervention \cite{geurts2022aversive}). Moreover, practice effects can harm reliability to the extent they manifest unequally across participants or minimize between-participant variability (i.e., ceiling effects). The repeatability of the Pavlovian go/no-go task has received little attention to date. The only exception is Moutoussis and colleagues \cite{moutoussis2018change} who observed diminished Pavlovian biases in retest performance at 6 and 18 months; however, this finding may reflect expected developmental changes \cite{raab2020adolescents, betts2020learning} rather than practice effects.

The objectives of the current study were to investigate the reliability and repeatability of a gamified version of the Pavlovian go/no-go task \cite{weber2022effects}. Gamification, or the incorporation of (video) game design elements into cognitive tasks, has previously been found to increase participant engagement \cite{sailer2017gamification} and improve the reliability of task measures \cite{kucina2022solution, verdejo2021unified}. Therefore, we hypothesized that our version of the Pavlovian go/no-go task would yield improvements in the test-retest reliability of model-based measures of task performance.

%In Experiment 1, a sample of N=103 participants completed the gamified task four times over one month. We used reinforcement learning models quantify Pavlovian biases in choice behavior. Contrary to our expectations, we observed large practice effects in participants' performance, including the virtual disappearance of Pavlovian biases, that in turn impacted the reliability of estimated model parameters. In Experiment 2, a sample of N=110 participants completed a modified version of the Pavlovian go/no-go task --- one that prevents participants from using alternative strategies to complete the task --- three times over two weeks. Here we observed comparably smaller practice effects and, crucially, acceptable reliability of estimated model parameters.

@@

A total of N=148 participants were recruited in May, 2020 from Amazon Mechanical Turk via CloudResearch \cite{litman2017turkprime} to participate in an online behavioral experiment. Participants were eligible to participate if they were at least 18 years old and resided in the United States. Following best practice recommendations \cite{robinson2019tapped}, no other inclusion criteria were applied. This study was approved by the Institutional Review Board of Princeton University (\#5291) and all participants provided informed consent. Total study duration was 15--20 minutes. Participants received monetary compensation for their time (rate: USD \$12/hr), plus an incentive-compatible bonus up to \$1.50 based on task performance.

@@

In each session, after providing consent, participants started by completing several self-report questionnaires (see Supplementary Materials for details). These measures were included for exploratory analyses not reported here. Next, participants completed a gamified version of the Pavlovian go/no-go task. In the task, participants observed different `robot' stimuli (Figure \ref{fig:task_schematic}A). On every trial, a robot was shown traveling down a conveyer belt into a `scanner'. Once inside, participants had 1.5 seconds to decide to either `repair' the robot by pressing the space bar (Go response) or press nothing (No-Go response). Participants were told that they would see different types of robots (indicated by a symbol on the robots' chestplates), and that their goal was to learn the correct response (Go, No-Go) for each robot type based on feedback (points won/lost) following their actions.

The task involved four trial types that differed in their correct action (Go, No-Go) and outcome domain (reward, punishment; Figure \ref{fig:task_schematic}B). Specifically, the four trial types were: go to win points (GW); no-go to win points (NGW); go to avoid losing points (GAL); and no-go to avoid losing points (NGAL). Note that GW and NGAL trials are Pavlovian-instrumental `congruent', because there is a match between the correct response and the expected approach/avoidance bias for each, whereas NGW and GAL trials are Pavlovian-instrumental `incongruent'. For the rewarding trials (GW, NGW), the possible outcomes were +10 or +1 points; for the punishing trials (GAL, NGAL), they were -1 or -10 points. The outcome domain of each robot was explicitly signaled to participants by a blue or orange `scanner light' (randomized within participants across sessions). Outcomes were probabilistic such that participants received the better of the two possible outcomes with 80\% chance if they made the correct action, and received the worse of the possible outcomes with 80\% chance if they made the incorrect action (Figure \ref{fig:task_schematic}C).

Participants saw eight unique robots across the task. Each individual robot was presented for 30 trials (240 trials total; Figure \ref{fig:task_schematic}D). Trials were divided into two blocks with four robots (one of each trial type) per block. Prior to task start, participants were required to review instructions, correctly answer five comprehension questions, and complete several practice trials. Failing to correctly answer all comprehension items forced the participant to reread sections of the instructions. Participants were provided a break between blocks. After completing the task, participants appraised the task along three dimensions: difficulty, fun, and clarity of instructions (see Table \ref{tab:appraisals}). The task was programmed in jsPsych \cite{de2015jspsych} and distributed using custom web-application software (see Code Availability).

@@

We first evaluated participants' choice behavior using five performance indices: overall percent correct responses; go bias, or the difference in correct responses between go and no-go trials; outcome bias, or the difference in correct responses between rewarding and punishing trials; Pavlovian bias, or the difference in correct responses between Pavlovian-instrumental congruent and incongruent trials; and feedback sensitivity, or the difference in correct responses between trials following veridical or sham feedback. For each session and index, we tested if the median value across participants was significantly different than zero (or 50\% for overall percent correct responses). We use the median due to skew in the performance indices. We also tested if the median value of each index was significantly different between each pair of sessions. P-values were derived via permutation testing, where a null distribution of values were obtained by permuting the condition labels (for within-session tests) or session labels (for between-session tests) 5000 times. Within-session tests were not corrected for multiple comparisons as each test constitutes an individual hypothesis test; between-session tests were corrected for multiple comparisons using the familywise error rate correction \cite{winkler2014permutation}.

@@

We fit a set of seven nested reinforcement learning (RL) models to participants' choice data. All models are variants of the Rescorla-Wagner model and have previously been used to predict choice behavior on this task \cite{guitart2012go, mkrtchian2017modeling, moutoussis2018change, swart2017catecholaminergic}. In the base model (M1), the probability a participant chooses an action in response to stimulus $k$ is determined by the difference in stimulus-action values ($Q_k(\text{Go}) - Q_k(\text{No-Go}))$, scaled an outcome sensitivity parameter ($\beta$), and passed through the logistic function. In turn, stimulus-action values are learned via the Rescorla-Wagner update rule as governed by a learning rate ($\eta$). Model 2 is augmented with a single static approach/avoidance parameter ($\tau$) that biases action towards Go responses if $\tau_j > 0$ and No-Go responses if $\tau < 0$. The succeeding model (M3) has independent approach/avoidance parameters per outcome domain ($\tau_+$, $\tau_-$). Models 4 and 5 have either independent outcome sensitivity ($\beta_+$, $\beta_-$; M4) or learning rate parameters ($\eta_+$, $\eta_-$; M5) per outcome domain. In Model 6, all three parameter types are independent across outcome domains. Finally, the most complex model (M7) includes a lapse rate ($\xi$). Complete model equations and descriptions are provided in the Supplementary Materials.

@@

Trial-by-trial choice behavior for each session is presented in Figure \ref{fig:exp01_behavior}A. Performance in the first session qualitatively conformed to the expected pattern of results, i.e., worse performance on Pavlovian-instrumental incongruent trials. However, this effect was ostensibly diminished in all follow-up sessions. We turn to the descriptive analyses to formally test these trends.

The group-averaged performance indices per session are summarized in Figure \ref{fig:exp01_behavior}B. On Day 0, the overall percent correct responses was 85.0\%. Performance improved in all subsequent sessions. Pairwise comparisons confirmed that performance was indeed worse on Day 0 compared to each follow-up session (all $p < 0.001$); no other comparisons were significant. Participants' self-reported mood and anxiety were largely stable over the same period (Figure \ref{fig:figS05}), indicating this shift in performance more likely reflects practice effects rather than changes in participants' state.

Across sessions, participants made more correct responses on go trials than no-go trials. The go bias was significantly reduced in all follow-up sessions compared to Day 0 (all $p < 0.001$); so too was the bias on Day 28 compared to Day 3 ($p < 0.001$). Similarly, participants made more correct responses on Pavlovian-congruent than incongruent trials. Again, the Pavlovian bias was significantly reduced in all follow-up sessions compared to Day 0 (all $p < 0.001$); no other comparisons were significant. Participants made marginally more correct responses on rewarding trials on Day 3 only.

@@

Trial-by-trial choice behavior for each session is presented in Figure \ref{fig:exp02_behavior}A. In contrast to Experiment 1, performance in each session qualitatively conformed to the expected pattern of results. The group-averaged performance indices per session are summarized in Figure \ref{fig:exp02_behavior}B. On Day 0, overall percent correct responses was 67.5\%. Performance improved in all subsequent sessions, but only marginally so. Pairwise comparisons confirmed that performance was significantly greater on Day 3 compared to Day 0 ($p = 0.009$); however, no other comparisons were significant.

@@

In all sessions, participants performed better on go trials than no-go trials. The go bias on Day 0 was significantly greater than that for all other sessions (all $p < 0.005$); no other comparisons were significant. Participants also performed better on Pavlovian congruent compared to incongruent trials in all sessions. The Pavlovian bias on Day 0 was significantly greater than that for all other sessions (both $p = 0.027$); no other comparisons were significant. In sum, group-averaged behavior showed evidence of practice effects but these were minor by comparison to those observed in Experiment 1.

A similar pattern of results was observed for feedback sensitivity. Across sessions, participants made more correct responses following veridical compared to sham feedback. No pairwise comparison was significant (all $p > 0.10$), suggesting that feedback sensitivity was largely conserved across sessions.

@@

The current study is not without limitations. Here we have only investigated the psychometric properties of our modified Pavlovian go/no-go task in a sample of online adult participants. The reliability of task measures, however, are not absolute; reliability can vary by participant demographics and the experiment setting. For example, previous studies have found that the reliability of specific task measures in healthy adults is not the same as for adults with psychopathology \cite{cooper2017role} or healthy children \cite{arnon2020current}. To the extent that our modified version of the Pavlovian go/no-go task is more challenging (see \ref{tab:appraisals}), it may be the case that it proves too challenging for other groups, which may harm reliability (e.g., \cite{arnon2020current}). Additional studies are necessary to validate this version of the task in other populations. It should also be noted that the current study is not necessarily informative about the reliability of Pavlovian biases over longer periods of time (i.e., beyond 2--4 weeks).

@@

\section*{Citation diversity statement}

Recent work in several fields of science has identified a bias in citation practices such that papers from women and other minority scholars are under-cited relative to the number of such papers in the field \cite{dworkin2020extent, bertolero2020racial}. Here we sought to proactively consider choosing references that reflect the diversity of the field in thought, form of contribution, gender, race, ethnicity, and other factors. First, we obtained the predicted gender of the first and last author of each reference by using databases that store the probability of a first name being carried by a woman \cite{dworkin2020extent}. By this measure and excluding self-citations to the first and last authors of our current paper), our references contain 12.0\% woman(first)/woman(last), 16.0\% man/woman, 26.0\% woman/man, and 46.0\% man/man. This method is limited in that a) names, pronouns, and social media profiles used to construct the databases may not, in every case, be indicative of gender identity and b) it cannot account for intersex, non-binary, or transgender people. Second, we obtained predicted racial/ethnic category of the first and last author of each reference by databases that store the probability of a first and last name being carried by an author of color \cite{ambekar2009name, sood2018predicting}. By this measure (and excluding self-citations), our references contain 4.7\% author of color (first)/author of color(last), 14.1\% white author/author of color, 18.2\% author of color/white author, and 63.0\% white author/white author. This method is limited in that a) names and Florida Voter Data to make the predictions may not be indicative of racial/ethnic identity, and b) it cannot account for Indigenous and mixed-race authors, or those who may face differential biases due to the ambiguous racialization or ethnicization of their names.  We look forward to future work that could help us to better understand how to support equitable practices in science.

@@

\begin{table}[h!]
    \centering
    \begin{tabular}{lccccc}
    \toprule
               & Study &   Day 0 &      Day 3 &     Day 14 &     Day 28 \\
    \midrule
    Difficulty &  1 &  2.5 (1.1) &  2.2 (0.9) &  2.1 (1.0) &  1.8 (0.8) \\
               &  2 &  3.3 (1.1) &  3.0 (1.1) &  3.1 (1.1) &          - \\
    \midrule
    Fun        &  1 &  3.9 (0.9) &  4.0 (1.0) &  3.9 (0.9) &  4.1 (0.9) \\
               &  2 &  3.9 (0.9) &  4.1 (0.8) &  4.0 (0.8) &          - \\
    \midrule
    Clarity    &  1 &  4.8 (0.6) &  4.9 (0.4) &  5.0 (0.2) &  4.9 (0.3) \\
               &  2 &  4.9 (0.5) &  4.9 (0.2) &  4.9 (0.2) &          - \\
    \bottomrule
    \end{tabular}
    \caption{Mean (sd) of participants' ratings of task difficulty, fun, and clarity. All ratings were made on a 5-point Likert scale. Difficulty: ``How difficult was the task?'' (Very easy = 1, Very hard = 5); Fun: ``How fun was the task?'' (Very boring = 1, Very fun = 5); Clarity: ``How clear were the instructions?'' (Very confusing = 1, Very Clear = 5).}
    \label{tab:appraisals}
\end{table}

@@

\clearpage
\subsection*{ahahahhahha}
